Tropical Andes plant species BIEN data

### 2023-07-25 code/L0/L0_TropicalAndes_plants_BIEN_occ.Rmd
update summary and species list code

# Read in IUCN data
Data was obtained from https://www.iucnredlist.org/search?permalink=9621ab77-2341-4bf8-9557-b7f19f7f2a35
```{r}
plants_habitats <- read.csv(file.path(data_path,"IUCN/Tropical Andes Plants - Search Results/habitats.csv"))
```

# Create species list from IUCN data
```{r}
plant_species <- unique(plants_habitats$scientificName)
```

# List of countries of interest
```{r}
country_vector <- c("Ecuador", "Venezuela", "Peru", "Colombia", "Bolivia")
```

# Get occurrence data for Tropical Andes from BIEN database
```{r}
TropicalAndes_BIEN_occ <- BIEN_occurrence_country(country = country_vector, all.taxonomy = TRUE, observation.type = TRUE, political.boundaries = TRUE, collection.info = TRUE)

# species list
TropicalAndes_BIEN_species_list <- BIEN_list_country(country = country_vector)
```

@@

```{r}
glimpse(TropicalAndes_BIEN_species_list)
```

@@

TropicalAndes_BIEN_species_list_path <- file.path(output_path, "TropicalAndes_BIEN_plant_species_list.csv")
write.csv(TropicalAndes_BIEN_species_list, file = TropicalAndes_BIEN_species_list_path)
```

>>>>

# Get occurrence data for Tropical Andes from BIEN database
```{r}
TropicalAndes_BIEN_occ_ec <- BIEN_occurrence_country(country = "Ecuador", all.taxonomy = TRUE, observation.type = TRUE, political.boundaries = TRUE, collection.info = TRUE)

TropicalAndes_BIEN_occ_ve <- BIEN_occurrence_country(country = "Venezuela", all.taxonomy = TRUE, observation.type = TRUE, political.boundaries = TRUE, collection.info = TRUE)

TropicalAndes_BIEN_occ_pe <- BIEN_occurrence_country(country = "Peru", all.taxonomy = TRUE, observation.type = TRUE, political.boundaries = TRUE, collection.info = TRUE)

TropicalAndes_BIEN_occ_co <- BIEN_occurrence_country(country = "Colombia", all.taxonomy = TRUE, observation.type = TRUE, political.boundaries = TRUE, collection.info = TRUE)

TropicalAndes_BIEN_occ_bo <- BIEN_occurrence_country(country = "Bolivia", all.taxonomy = TRUE, observation.type = TRUE, political.boundaries = TRUE, collection.info = TRUE)
```

```{r}
# combine occ

```

@@

```{r}
print("The number of records is")
nrow(TropicalAndes_BIEN_occ)
print("The number of species is")
length(unique(TropicalAndes_BIEN_occ$scrubbed_species_binomial))
print("The number of families is")
length(unique(TropicalAndes_BIEN_occ$family_matched))
```

# Extract species list
```{r}
BIEN_occ_SpeciesList <- unique(TropicalAndes_BIEN_occ$scrubbed_species_binomial)
```

@@

TropicalAndes_BIEN_species_list_path <- file.path(output_path, "TropicalAndes_BIEN_plant_occ_species.csv")
write.csv(TropicalAndes_BIEN_species_list, file = TropicalAndes_BIEN_species_list_path)
```
